Hippocampal replay of experience at real world speeds

### 2021-05-13 Article.tex

Recognizing the problems with the linear fit, several studies have moved away from the constant velocity assumption, using the most probable location at each time bin \citep{}. For example, using this approach, \cite{PfeifferAutoassociativedynamicsgeneration2015} found that awake replays can alternate between representing a single location and sequential spatial trajectories. On the other hand, \cite{StellaHippocampalReactivationRandom2019} reported that replays during sleep are spatially continuous and follow Brownian diffusion dynamics. However, both methods still used large time bins and neither took into account the uncertainty of the decoded estimates, making it hard to identify the source of the different conclusions.

>>>>

Recognizing the problems with the linear fit, several studies have moved away from the constant velocity assumption, using the most probable location at each time bin \citep{KaeferReplayBehavioralSequences2020, CareyRewardrevaluationbiases2019, GrosmarkDiversityneuralfiring2016, WuHippocampalReplayCaptures2014, PfeifferHippocampalplacecellsequences2013}. For example, using this approach, \cite{PfeifferAutoassociativedynamicsgeneration2015} found that awake replays can alternate between representing a single location and sequential spatial trajectories. On the other hand, \cite{StellaHippocampalReactivationRandom2019} reported that replays during sleep are spatially continuous and follow Brownian diffusion dynamics. However, both methods still used large time bins and neither took into account the uncertainty of the decoded estimates, making it hard to identify the source of the different conclusions.
